Typing a linear \picalc

### 2020-04-11 paper/paper.tex
Rewrite the intro to the typing system

\todo{why do we use a single relation for both type judgements and usage judgments}

A type system is in the business of further constraining a language, filtering out terms that (although well-formed) are meaningless.
In the simply typed \lambdacalc{}, a term has a meaning iff it has a type.
This typing judgment is a proof of the form $\Gamma \vdash t : T$, where the term $t$ has type $T$ under the typing context $\Gamma$ -- the typing context associates variables (possibly occurring within $t$) to types.
In the simply typed \picalc{} however, it is the channels that are typed, and a process has a meaning iff it \emph{uses} its channels according to their types.
The typing judgment is therefore of the form $\Gamma \vdash p$, where the process $p$ (which has no type of its own) uses the channels in $\Gamma$ according to their types.

A resource-aware type system uses both types and usage counting to constraint a language.
It uses typing contexts to keep track of both types and usage counts.
In the case of a linear type system, resources must be used exactly once, and usages transition from available to consumed as soon as they are used.
In the linear \picalc{} however, every channel must be used exactly once to receive and exactly once to send.
In \S \ref{multiplicities}, we generalize this usage counting algebra so that the same type system can be used for a combination of linear, shared, and gradual types.

Syntax directed
Continuations.
\ref{leftover-typing}

@@

\subsection{Contexts}

>>>>

A \emph{resource-aware} typing system for the \emph{\picalc{}} is distinctive in several ways.

\begin{description}
  \item [As a resource-aware typing system,] the language is constrained not just by types, but also by their usage annotations.
    We must be able to add up and split usage contexts, to do so we introduce a generalized algebra in \S \ref{multiplicities}.
    We provide an independent inductive definition of typing contexts and usage contexts in \S \ref{contexts}.
    \todo{why independent}

  \item [As a typing system for the \picalc{},] the terms (processes) in the typing judgment do not come accompanied by a type -- processes have no type.
    It is the communication channels that are annotated with types and usages.
    Typing judgments assert that the process correctly uses the channels in the context under which it is typed.
\end{description}

In this paper, we combine typing and annotation judgments into a single judgment.
Although the typing rules are for now completely syntax-directed, adding support for branching would introduce choice in the typing derivations.
If we were to keep typing judgments and annotation judgments separate, we would need a coherence relation making sure that the same choice is taken by both.
We avoid doing so by combining them into a single judgment.

We make use \emph{leftover typing}, a technique consisting of adding an \emph{output context of usages} to the usual \emph{input context of usages}.
This output context contains the leftovers: the multiplicities unused by the processes.
Crucially, this output context can then be used as the input context of the continuation process.
The typing rules are introduced in \S \ref{leftover-typing}.

@@

\subsection{Contexts}
\label{contexts}
